---
title: "Edinburgh Markdown"
output: html_document
---


```{r,echo=FALSE,warning=FALSE,message=FALSE}
# Load libraries
library(rgdal)
library(leaflet)
library(tidyverse)
library(rgeos)
library(raster)
library(ggplot2)
library(sf)
library(mapview)
library(maptools)
library(sp)
library(readxl)
library(readr)
library(grid)
library(gridExtra)
library(xtable)
library(knitr)
library(kableExtra)
library(plyr)
library(RColorBrewer)

#1.Function for keeping data of Edinburgh with speed limits 20/30/40
filter_data <- function(data){
  data <- data %>% filter(data$Speed_limit %in% c(20,30,40)) 
  data <- data %>% filter(data$`Local_Authority_(District)` == 923)
  #data$Date <- as.Date(data$Date,format="%d/%m/%Y")
  data <- na.omit(data[1:31])#remove NA obs
  return(data)
}

#2.Function for deleting Na points
delete_na <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}

##1.Data path 
#dir_path <- "V:\\Studies\\MOVED\\HealthImpact\\Data\\"
dir_path <- "C:\\Users\\Kyriaki Kokka\\Desktop\\"
```


```{r,echo=FALSE,warning=FALSE,message=FALSE}

#Read control zones codes
control_1 <- read.delim(paste0(dir_path, "20mph study collisions\\control_zone_codes\\controlzone1.txt"),stringsAsFactor = FALSE,header = FALSE)
control_3 <- read.delim(paste0(dir_path, "20mph study collisions\\control_zone_codes\\controlzone3.txt"),stringsAsFactor = FALSE,header = FALSE)
control_4 <- read.delim(paste0(dir_path, "20mph study collisions\\control_zone_codes\\controlzone4.txt"),stringsAsFactor = FALSE,header = FALSE)
control_5 <- read.delim(paste0(dir_path, "20mph study collisions\\control_zone_codes\\controlzone5.txt"),stringsAsFactor = FALSE,header = FALSE)
control_6 <- read.delim(paste0(dir_path, "20mph study collisions\\control_zone_codes\\controlzone6.txt"),stringsAsFactor = FALSE,header = FALSE)
control_7 <- read.delim(paste0(dir_path, "20mph study collisions\\control_zone_codes\\controlzone7.txt"),stringsAsFactor = FALSE,header = FALSE)

#Path for control zones
control_gdb_path <- paste0(dir_path, "20mph study collisions\\control zones")
control_gdb_layers <- ogrListLayers(control_gdb_path)

#Read data
edin_control_zone <- readOGR(dsn = control_gdb_path,layer="SG_DataZone_Bdry_2011", verbose = FALSE)
edin_control_zone <- spTransform(edin_control_zone, "+init=epsg:4326")

```

>Edinburgh's road network

```{r,echo=FALSE,warning=FALSE,message=FALSE} 
#Data inputs

#2.Gis 
#Read geodatabase for Edinburgh
#Path
gdb_path <- paste0(dir_path, "20mph study collisions\\20mph.gdb")
gdb_layers <- ogrListLayers(gdb_path)

#Read shapefile
edin_cons_streets <- readOGR(dsn = gdb_path,layer="Consultation20mphStreets", verbose = FALSE)
#Put ID column as variable 
edin_cons_streets@data <-rowid_to_column(edin_cons_streets@data, "ID")
#Transform to long/lat
edin_cons_streets <- spTransform(edin_cons_streets, "+init=epsg:4326")
#Visualize with leaflet
col = c("#bf812d","#80cdc1","#d6604d","#525252","#1a9850","#cab2d6","#e6f598","#4393c3")
#my.palette <- brewer.pal(n = 8, name = "Set3")
spplot(edin_cons_streets,'LAYER',col.regions = col)
leaflet(edin_cons_streets) %>% addTiles() %>% addPolygons()


```

>Edinburgh's implementation zones

```{r,echo=FALSE,warning=FALSE,message=FALSE}
#Read shapefile
edin_impl_zones <- readOGR(dsn = gdb_path, layer="ImplementationZones", verbose = FALSE)
#Transform to long/lat
edin_impl_zones <- spTransform(edin_impl_zones, "+init=epsg:4326")
#Change zone 1
edin_impl_zones@data$ImplementationZone <- as.integer(edin_impl_zones@data$ImplementationZone)
edin_impl_zones@data[6,]$ImplementationZone <- 7
#Visualize with leaflet
#display.brewer.all()
my.palette <- brewer.pal(n = 7, name = "Pastel2")
spplot(edin_impl_zones,"ImplementationZone",col.regions = my.palette, cuts = 7)
leaflet(edin_impl_zones) %>% addTiles() %>% addPolygons()
```



```{r,echo=FALSE,warning=FALSE,message=FALSE} 
#Read data
edin_road_data <- read_csv(paste0(dir_path, "20mph study collisions\\cleaned datasets\\edin_road_data.csv"))
control_zone_data <- read_csv(paste0(dir_path, "20mph study collisions\\cleaned datasets\\edin_control_data.csv"))
casualties_data <- read_csv(paste0(dir_path, "20mph study collisions\\cleaned datasets\\edin_casualties_data.csv"))
rd_2019 <- read_csv(paste0(dir_path, "20mph study collisions\\cleaned datasets\\data2019.csv"))

edin_road_data <- edin_road_data %>% mutate(year = format(as.Date(edin_road_data$Date, format="%m/%d/%Y"),"%Y"))
edin_road_data <- rbind.fill(edin_road_data,rd_2019)
casualties_data <- rbind.fill(casualties_data,rd_2019)
#keep a copy for implementation zones
data <- edin_road_data
edin_road_data <-rowid_to_column(edin_road_data, "ID")

df <- data
data <- rowid_to_column(data,"index_ID")
```

>Time series analysis

```{r, echo=FALSE, warning=FALSE,message=FALSE}
ggplot(edin_road_data) +
 aes(x = Speed_limit) +
 geom_histogram(bins = 30L, fill = "#a6d96a") +
 theme_minimal() +
 facet_wrap(vars(year))

ggplot(edin_road_data) +
 aes(x = Date, colour = Speed_limit) +
 geom_histogram(bins = 30L, fill = "#a6d96a") +
 scale_color_distiller(palette = "Greens") +
 theme_minimal()

ggplot(edin_road_data) +
 aes(x = Date, weight = Speed_limit) +
 geom_bar(fill = "#1a9850") +
 theme_minimal()
```


```{r, echo=FALSE, warning=FALSE,message=FALSE}
#Functions for the analysis
#Function for the nearest line
nearest_line <-function(df,road_net){
  #Create planar(cartesian) projection 
  crs <- CRS( "+proj=utm +zone=32 +ellps=WGS72 +units=m +no_defs")     # UTM zone = 32 N
  wgs84 <- CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")  # long/lat
  
  #Convert data to planar projection  
  road_net <- spTransform(road_net,crs)
  df <-  spTransform(SpatialPointsDataFrame(coords = df[5:6],proj4string = wgs84,data = df), crs)
  
  #Make sure our data have same projections
  proj4string(df) <- proj4string(road_net)
  
  #Find nearest line with maxDist=6m 
  nearest_line_sp <- localSnapPointsToLines(df,road_net,maxDist=6,withAttrs=TRUE)
  
  return(nearest_line_sp)
}

#Function for leaflet visualisations
leaflet_map <- function(final_df,road_df,edin_streets){
  crs <- CRS( "+proj=utm +zone=32 +ellps=WGS72 +units=m +no_defs")     # UTM zone = 32 N
  wgs84 <- CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")  # long/lat
  
  #Convert data to planar projection  
  edin_streets <- spTransform(edin_streets,crs)
  coordinates(road_df) <- ~ Longitude + Latitude
  coordinates(final_df) <- ~ X + Y
  
  #Convert data projections back to lat/long to plot with leaflet
  edin_streets <- spTransform(edin_streets,"+init=epsg:4326")
  
  #Same projections
  proj4string(final_df) <- proj4string(edin_streets)
  proj4string(road_df) <- proj4string(edin_streets)
  
  edin_streets <- st_as_sf(edin_streets)
  #Leaflet maps of the road network , accidents and their projections
  road_existing_20 <-edin_streets%>% filter(edin_streets$LAYER == "20mph existing streets")
  road_local_20 <- filter(edin_streets, edin_streets$LAYER == "20mph local streets")
  road_main_20 <- filter(edin_streets, edin_streets$LAYER == "20mph main streets")
  road_30 <- filter(edin_streets, edin_streets$LAYER == "30mph")
  road_40 <- filter(edin_streets, edin_streets$LAYER == "40mph")
  road_part <- filter(edin_streets, edin_streets$LAYER == "Part time 20mph")
  road_50 <- filter(edin_streets, edin_streets$LAYER == "50, 60 or 70mph")
  road_trunk <- filter(edin_streets, edin_streets$LAYER == "Trunk roads")
  
  
  #Visualize
  map <- leaflet() %>% addTiles() %>% addPolygons(data = edin_streets)
  #map <- map %>%  addLegend("bottomright",colors =c("green",  "red", "yellow", "cyan", "blue","black","purple","orange"),
  #labels= c("existing 20mph", "local 20mph","main 20 mph","30mph","40mph", "part time 20mph","50,60 or 70mph","Trunk roads"),
  #title= "Road network",opacity = 1)
  map_near <-map %>% leaflet() %>% addTiles() %>% addMarkers(lng =final_df$X, lat = final_df$Y,
                                                             popup =paste("Accident index: ", final_df$Accident_Index, "<br>",
                                                                          "Speed limit: ", final_df$Speed_limit ,"<br>",
                                                                          "Layer: ",final_df$LAYER,"<br>",
                                                                          "Casualty severity: ",final_df$Casualty_Severity))
  road_df <- (data.frame(road_df))
  map3 <- map_near %>% addCircleMarkers(lng =road_df$Longitude , lat = road_df$Latitude,
                                        popup =paste("Accident index: ", road_df$Accident_Index, "<br>",
                                                     "Speed limit: ", road_df$Speed_limit ,"<br>",
                                                     "Casualty severity: ",road_df$Casualty_Severity ))
  

  map3 <- map3 %>% addLegend("bottomright",colors =c("green",  "red", "yellow", "cyan", "blue","black","purple","orange"),
                      labels= c("existing 20mph", "local 20mph","main 20 mph","30mph","40mph", "part time 20mph","50,60 or 70mph","Trunk roads"),
                      title= "Road network",opacity = 1)
  
  map3 %>%
  setView(lng = -3.188267 , lat = 55.953251, zoom = 11)%>%
    addPolylines(data = road_existing_20, color= "green")%>%
    addPolylines(data = road_local_20,color= "red")%>%
    addPolylines(data = road_main_20,color= "yellow")%>%
    addPolylines(data = road_30,color= "cyan")%>%
    addPolylines(data = road_40,color= "blue")%>%
    addPolylines(data = road_part,color= "black")%>%
    addPolylines(data = road_50,color= "purple")%>%
    addPolylines(data = road_trunk,color= "orange")
}

#Count function
count <- function(data_df){
  count1 <- aggregate(Accident_Index~LAYER,data_df,length)
  count2 <- aggregate(Accident_Index~Speed_limit,data_df,length)
  print(count1)
  print(count2)
}

count_pre <- function(data_df){
  count1 <-  aggregate(Accident_Index~LAYER,data_df,length)
  count2 <-  aggregate(Accident_Index~Speed_limit,data_df,length)
  #print(count1)
  #print(count2)
  return(count1)
}

count_impl <- function(data_df){
  count1 <- aggregate(Accident_Index~ImplementationZone,data_df,length)
  print(count1)
}
```

```{r, echo=FALSE, warning=FALSE,message=FALSE}
#Data manipulation
#Get nearest line for pre and post 20mph using the nearest_line function 
nearest_road <- nearest_line(edin_road_data,edin_cons_streets)
nearest_road <- spTransform(nearest_road,"+init=epsg:4326")
```

```{r, echo=FALSE, warning=FALSE,message=FALSE}
#Merge the dataframes based on the ID of the nearest line in order to connect geoinformation with stasts19
#Then merge Casualty severity column with collisions dataset
mergedDf <- merge(data.frame(nearest_road),edin_cons_streets@data,by.x = "nearest_line_id" ,by.y = "ID")
mergedDf <- merge(mergedDf,casualties_data,by.x = "Accident_Index" ,by.y = "Accident_Index")
mergedDf$Casualty_Severity <- as.character(mergedDf$Casualty_Severity)
mergedDf$Casualty_Severity[mergedDf$Casualty_Severity == 1] <- "Fatal"
mergedDf$Casualty_Severity[mergedDf$Casualty_Severity == 2] <- "Serious"
mergedDf$Casualty_Severity[mergedDf$Casualty_Severity == 3] <- "Slight"
mergedDf <- rename(mergedDf,c("Longitude.x" = "Longitude","Latitude.x"="Latitude","year.x"="year","Speed_limit.x"="Speed_limit"))
#mergedDf$Accident_Index <- as.character(mergedDf$Accident_Index)

```

>Mapping accidents with roads: 2013/14

```{r, echo=FALSE, warning=FALSE,message=FALSE}
leaflet_map(mergedDf[mergedDf$year == "2013", ],edin_road_data[edin_road_data$year == "2013", ],edin_cons_streets)
count(mergedDf[mergedDf$Date >="2013-07-31" & mergedDf$Date <= "2014-7-30", ])
```

>Mapping accidents with roads: 2014/15

```{r, echo=FALSE, warning=FALSE,message=FALSE}
leaflet_map(mergedDf[mergedDf$year == "2014", ],edin_road_data[edin_road_data$year == "2014", ],edin_cons_streets)
count(mergedDf[mergedDf$Date >="2014-07-31" & mergedDf$Date <= "2015-7-30", ])
```

>Mapping accidents with roads: 2015/16

```{r, echo=FALSE, warning=FALSE,message=FALSE}
leaflet_map(mergedDf[mergedDf$year == "2015", ],edin_road_data[edin_road_data$year == "2015", ],edin_cons_streets)
count(mergedDf[mergedDf$Date >="2015-07-31" & mergedDf$Date <= "2016-7-20", ])
```

>Mapping accidents with roads: 2018/2019

```{r, echo=FALSE, warning=FALSE,message=FALSE}
leaflet_map(mergedDf[mergedDf$year == "2018", ],edin_road_data[edin_road_data$year == "2018", ],edin_cons_streets)
count_pre(mergedDf[mergedDf$year == "2018", ]) + count_pre(mergedDf[mergedDf$year == "2019", ])
```

>Count pre 20mph

```{r,echo=FALSE,warning=FALSE,message=FALSE}
pre_20 <- count_pre(mergedDf[mergedDf$year == "2013", ]) + count_pre(mergedDf[mergedDf$year == "2014", ]) + count_pre(mergedDf[mergedDf$year == "2015", ])  
pre_20
```

>Count post 20mph

```{r,echo=FALSE,warning=FALSE,message=FALSE}
count_pre(mergedDf[mergedDf$year == "2018", ]) + count_pre(mergedDf[mergedDf$year == "2019", ])
```

>Output column: Layer

```{r,echo=FALSE,warning=FALSE,message=FALSE}
head(mergedDf[,c(1,20,40)])
```

>Table: Average annual road traffic collision rates in the city of Edinburgh (road network)

```{r, echo=FALSE, warning=FALSE, message=FALSE}
type <- c("Streets at 30mph","Streets at 20mph","Streets at 30mph changed to 20mph","Streets at 40mph","All streets")
collisions_pre_20mph <- c("606","351","1273","214","2444")
collisions_post_20mph <- c("223","98","400","89","810")
rate_pre_20mph <- c("0.25","0.14","0.52","0.09","1")
rate_post_20mph <- c("0.28","0.12","0.49","0.11","1")
diff_in_rates <- c("-0.03","0.02","0.03","-0.02","0")
percentage_diff_in_rates <- c("-12 %" ," 14.3 %"," 5,8 %","-22.2 %"," ")
df <- data.frame(type,collisions_pre_20mph,collisions_post_20mph,rate_pre_20mph,rate_post_20mph,diff_in_rates,percentage_diff_in_rates)

kable(df) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

>Table: Average annual road traffic collision rates in the city of Edinburgh (Stats19)

```{r,echo=FALSE,warning=FALSE,message=FALSE}
type <- c("Streets at 20mph","Streets at 30mph","Streets at 40mph","All streets")
collisions_pre_20mph <- c("96","2088","211","2395")
collisions_post_20mph <- c("428","309","99","836")
rate_pre_20mph <- c("0.04","0.87","0.09","1")
rate_post_20mph <- c("0.51","0.37","0.12","1")
diff_in_rates <- c("-0.47","0.50","-0.03","0")
percentage_diff_in_rates <- c("1175 %" ,"57.47 %","-33.3 %"," ")
df <- data.frame(type,collisions_pre_20mph,collisions_post_20mph,rate_pre_20mph,rate_post_20mph,diff_in_rates,percentage_diff_in_rates)

kable(df) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

> Effect estimate (GIS)

```{r,echo=FALSE,warning=FALSE,message=FALSE}
Tax_year <- c("Annual number of collisions"," ","Effect estimate ")
Y_2013_14 <- c("976"," "," 58.05")
Y_2014_15 <- c("901"," "," ")
Y_2015_16 <- c("567"," "," ")
Y_2018_19 <- c("810"," "," ")
df <- data.frame(Tax_year,Y_2013_14,Y_2014_15,Y_2015_16,Y_2018_19)

kable(df) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```

> Effect estimate (Stats19)

```{r,echo=FALSE,warning=FALSE,message=FALSE}
Tax_year <- c("Annual number of collisions"," ","Effect estimate ")
Y_2013_14 <- c("1000"," "," 27.85")
Y_2014_15 <- c("927"," "," ")
Y_2015_16 <- c("580"," "," ")
Y_2018_19 <- c("836"," "," ")
df <- data.frame(Tax_year,Y_2013_14,Y_2014_15,Y_2015_16,Y_2018_19)

kable(df) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```


```{r,echo=FALSE,warning=FALSE,message=FALSE}
#Create planar(cartesian) projection 
crs <- CRS( "+proj=utm +zone=32 +ellps=WGS72 +units=m +no_defs")     # UTM zone = 32 N
wgs84 <- CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")  # long/lat

#Convert data to planar projection  
edin_impl_zones <- spTransform(edin_impl_zones,crs)
utm_data <-  spTransform(SpatialPointsDataFrame(coords = data[5:6],proj4string = wgs84,data = data), crs)

proj4string(utm_data) <- proj4string(edin_impl_zones)

#add a buffer around the point
points_polygons <- gBuffer(utm_data, width=6, byid = TRUE )
count_zones <- over(points_polygons,edin_impl_zones,returnList = FALSE)
count_zones <- rowid_to_column(count_zones,"ID")

total_zones <- merge(data,count_zones,by.x="index_ID",by.y="ID")
df_zones <-data.frame(total_zones[2],total_zones[19],total_zones[36])

#Convert data projections back to lat/long to plot with leaflet
edin_impl_zones <- spTransform(edin_impl_zones,"+init=epsg:4326")
#total_zones <- spTransform(total_zones, "+init=epsg:4326")
utm_data <- spTransform(utm_data, "+init=epsg:4326")
#delete_na()
#df_na <- na.omit(df_zones[1:4]) # check how many are missing
```

>Mapping accidents with implementation zones: 2013

```{r,echo=FALSE,warning=FALSE,message=FALSE}

edin_impl_zones <- st_as_sf(edin_impl_zones)
#Leaflet maps of the zones & accidents
zone_1 <- filter(edin_impl_zones,edin_impl_zones$ImplementationZone == 1)
zone_2 <- filter(edin_impl_zones,edin_impl_zones$ImplementationZone == 2)
zone_3 <- filter(edin_impl_zones,edin_impl_zones$ImplementationZone == 3)
zone_4 <- filter(edin_impl_zones,edin_impl_zones$ImplementationZone == 4)
zone_5 <- filter(edin_impl_zones,edin_impl_zones$ImplementationZone == 5)
zone_6 <- filter(edin_impl_zones,edin_impl_zones$ImplementationZone == 6)
zone_7 <- filter(edin_impl_zones,edin_impl_zones$ImplementationZone == 7)

#Visualize
map_zones <- leaflet() %>% addTiles() %>% 
  addPolygons(data = zone_1, color= "green")%>%
  addPolygons(data = zone_2,color= "red")%>%
  addPolygons(data = zone_3,color= "purple")%>%
  addPolygons(data = zone_4,color= "cyan")%>%
  addPolygons(data = zone_5,color= "blue")%>%
  addPolygons(data = zone_6,color= "orange")%>%
  addPolygons(data = zone_7,color= "black")

map_zones <- map_zones %>% addLegend("bottomright",colors =c("green",  "red","purple", "cyan", "blue","orange","black"),
                      labels= c("1:City Centre", "2:North","3:South Central/East","4:North West","5:West", "6:South","7:Rural West"),
                      title= "Implementation zones",opacity = 1) %>% setView(lng = -3.188267 , lat = 55.953251, zoom = 11)

total <- total_zones[total_zones$year == "2013", ]

map_zones %>% addMarkers(lng =total$Longitude, lat = total$Latitude, 
                         popup =paste("Accident index: ", total$Accident_Index, "<br>",
                                      "Zone: ", total$ImplementationZone))
count_impl(total[total$year == "2013", ])
```

>Mapping accidents with implementation zones: 2014

```{r,echo=FALSE,warning=FALSE,message=FALSE}
total <- total_zones[total_zones$year == "2014", ]

map_zones %>%
  setView(lng = -3.188267 , lat = 55.953251, zoom = 11)%>%
  addMarkers(lng =total$Longitude, lat = total$Latitude, 
             popup =paste("Accident index: ", total$Accident_Index, "<br>",
                          "Zone: ", total$ImplementationZone))
count_impl(total[total$year == "2014", ])
``` 

>Mapping accidents with implementation zones: 2015

```{r,echo=FALSE,warning=FALSE,message=FALSE}
total <- total_zones[total_zones$year == "2015", ]

map_zones %>% addMarkers(lng =total$Longitude, lat = total$Latitude, 
                         popup =paste("Accident index: ", total$Accident_Index, "<br>",
                                      "Zone: ", total$ImplementationZone))
count_impl(total[total$year == "2015", ])
```

>Mapping accidents with implementation zones: 2016

```{r, echo=FALSE, warning=FALSE,message=FALSE}
total <- total_zones[total_zones$year == "2016", ]

map_zones %>% addMarkers(lng =total$Longitude, lat = total$Latitude, 
                         popup =paste("Accident index: ", total$Accident_Index, "<br>",
                                      "Zone: ", total$ImplementationZone))
count_impl(total[total$year == "2016", ])
```

>Mapping accidents with implementation zones: 2018

```{r,echo=FALSE,warning=FALSE,message=FALSE}
total <- total_zones[total_zones$year == "2018", ]

map_zones %>% addMarkers(lng =total$Longitude, lat = total$Latitude, 
                         popup =paste("Accident index: ", total$Accident_Index, "<br>",
                                      "Zone: ", total$ImplementationZone))
count_impl(total[total$year == "2018", ])
```

>Mapping accidents with implementation zones: 2019

```{r, echo=FALSE, warning=FALSE,message=FALSE}
total <- total_zones[total_zones$year == "2019", ]

map_zones %>% addMarkers(lng =total$Longitude, lat = total$Latitude, 
                         popup =paste("Accident index: ", total$Accident_Index, "<br>",
                                      "Zone: ", total$ImplementationZone))
count_impl(total[total$year == "2019", ])
```

>Output column: Implementation Zone

```{r,echo=FALSE,warning=FALSE,message=FALSE}
head(df_zones)
```

>Count accidents in control zones

```{r,echo=FALSE,warning=FALSE,message=FALSE}
buffer_data <-function(data,zone){
  #Create planar(cartesian) projection 
  crs <- CRS( "+proj=utm +zone=32 +ellps=WGS72 +units=m +no_defs")     # UTM zone = 32 N
  wgs84 <- CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")  # long/lat
  
  zone <- spTransform(zone,crs)
  data <-  spTransform(SpatialPointsDataFrame(coords = data[4:5],proj4string = wgs84,data = data), crs)
  
  proj4string(data) <- proj4string(zone)
  points <- gBuffer(data, width=6, byid = TRUE )
  count <- over(points,zone,returnList = FALSE)
  return(nrow(unique(count)))
}
```

> Control zone 1a:City center --> George St/Harbour, Aberdeen 

```{r,echo=FALSE,warning=FALSE,message=FALSE}
control_zone_1 <- edin_control_zone[edin_control_zone@data$DataZone %in%  control_1,]
con_data <- control_zone_data %>% filter(control_zone_data$`Local_Authority_(District)` %in% c("910"))
leaflet(control_zone_1) %>% addTiles() %>% addPolygons() %>% addMarkers(lng = con_data$Longitude, lat = con_data$Latitude) %>% setView(lng = -2.099075 , lat = 57.149651, zoom = 11)
buffer_data(con_data,control_zone_1)

```

> Control zone 1b:Rural west --> Tay Bridgehead & St Andrews

```{r,echo=FALSE,warning=FALSE,message=FALSE}
control_zone_7 <- edin_control_zone[edin_control_zone@data$DataZone %in%  control_7,]
con_data <- control_zone_data %>% filter(control_zone_data$`Local_Authority_(District)` %in% c("925"))
leaflet(control_zone_7) %>% addTiles() %>% addPolygons()%>% addMarkers(lng = con_data$Longitude, lat = con_data$Latitude) %>% setView(lng = -2.8833 , lat = 56.3833, zoom = 11)
buffer_data(con_data,control_zone_7)
```

> Control zone 3:South central --> Dundee

```{r,echo=FALSE,warning=FALSE,message=FALSE}
control_zone_3 <- edin_control_zone[edin_control_zone@data$DataZone %in%  control_3,]
con_data <- control_zone_data %>% filter(control_zone_data$`Local_Authority_(District)` %in% c("918"))
leaflet(control_zone_3) %>% addTiles() %>% addPolygons()%>% addMarkers(lng = con_data$Longitude, lat = con_data$Latitude)
buffer_data(con_data,control_zone_3)
```

> Control zone 4:North west -> Renfrew North, Renfrew South & Gallowhill, Paisley North West

```{r,echo=FALSE,warning=FALSE,message=FALSE}
control_zone_4 <- edin_control_zone[edin_control_zone@data$DataZone %in%  control_4,]
con_data <- control_zone_data %>% filter(control_zone_data$`Local_Authority_(District)` %in% c("935"))
leaflet(control_zone_4) %>% addTiles() %>% addPolygons()%>% addMarkers(lng = con_data$Longitude, lat = con_data$Latitude)
buffer_data(con_data,control_zone_4)
```

> Control zone 5:West --> Glasgow Kelvin

```{r,echo=FALSE,warning=FALSE,message=FALSE}
control_zone_5 <- edin_control_zone[edin_control_zone@data$DataZone %in%  control_5,]        
con_data <- control_zone_data %>% filter(control_zone_data$`Local_Authority_(District)` %in% c("926"))
leaflet(control_zone_5) %>% addTiles() %>% addPolygons()%>% addMarkers(lng = con_data$Longitude, lat = con_data$Latitude) %>% setView(lng = -4.25763 , lat = 55.86515, zoom = 11)
buffer_data(con_data,control_zone_5)
```

> Control zone 6:South --> Paisley

```{r,echo=FALSE,warning=FALSE,message=FALSE}
control_zone_6 <- edin_control_zone[edin_control_zone@data$DataZone %in%  control_6,]    
con_data <- control_zone_data %>% filter(control_zone_data$`Local_Authority_(District)` %in% c("926"))
leaflet(control_zone_6) %>% addTiles() %>% addPolygons() %>% addMarkers(lng = con_data$Longitude, lat = con_data$Latitude)
buffer_data(con_data,control_zone_6)
```

>Updated dataset for Edinburgh

```{r,echo=FALSE,warning=FALSE,message=FALSE}
#final_dataset
merged_1 <- mergedDf[,-c(34:38,39)]
total_zones_1 <- total_zones[,-c(1,3:34)]
updated_dataset <- merge(merged_1,total_zones_1,by.x="Accident_Index",by.y="Accident_Index")
updated_dataset <-updated_dataset[,-c(2,3)]
head(updated_dataset[,c(1,18,32,42)])
#Create new csv file with the cleaned data
write.csv(updated_dataset, file = paste0(dir_path, "20mph study collisions\\cleaned datasets\\final_Edinburgh_data.csv"),row.names=FALSE)

```

