---
title: "Belfast_md"
author: "edin"
date: "7/2/2020"
output: html_document
---


```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(rgdal)
library(leaflet)
library(tidyverse)
library(rgeos)
library(raster)
library(ggplot2)
library(sf)
library(mapview)
library(maptools)
library(sp)
library(readxl)
library(readr)
library(knitr)
library(kableExtra)
library(plyr)
source('../functions/localSnapPointsToLines.R')
source('../functions/nearest_line_belf.R')
source('../functions/read_belf_controldata.R')
source('../functions/time_plot_belf.R')
source('../functions/belcount.R')
source('../functions/read_bel_data.R')
source('../functions/belcount_pre.R')
source('../functions/read_belfcontrol_zone.R')
source('../functions/delete_na.R')
source('../functions/belcount_pre.R')
source('../functions/read_belf_road.R')
source('../functions/leaflet_map_belf.R')
source('../functions/read_belf_impl_zones.R')
source('../functions/belf_annual_table.R')
source('../functions/buffer_data.R')
source('../functions/belf_leaflet_zones.R')
# Define network dir path
dir_path <- "../data"
```


```{r, echo=FALSE, warning=FALSE, message=FALSE}
#Belfast Road Network
#Belfast SA
#Belfast OA
#gdb_path <- paste0(dir_path, "/Belfast Road Network")
#gdb_layers <- ogrListLayers(gdb_path)

#Read shapefile
#belf_streets <- readOGR(dsn = gdb_path,layer="Belfast_Road_Network", verbose = FALSE)
#belf_streets <- spTransform(belf_streets, "+init=epsg:4326")
#leaflet(belf_streets) %>% addTiles() %>% addPolylines() %>% setView(lng = -5.926437 , lat = 54.607868, zoom = 14)
```

> Belfast road network changed to 20mph

```{r ,echo=FALSE, warning=FALSE, message=FALSE, comment=FALSE}
#Road data 
belfast_road_data <- read_belf_road(dir_path)
leaflet(belfast_road_data) %>% addTiles() %>% addPolylines() %>% setView(lng = -5.926437 , lat = 54.607868, zoom = 14)
```

> Belfast city center implementation zone

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#Output Areas 
belf_impl_zones_out <- read_belf_impl_zones(dir_path)
leaflet(belf_impl_zones_out) %>% addTiles() %>% addPolygons()
```

> Belfast metropolitan area

```{r, echo=FALSE, warning=FALSE, message=FALSE}
gdb_path_out <- paste0(dir_path, "/Belfast SA")
gdb_layers <- ogrListLayers(gdb_path_out)

belf_metr_area <- readOGR(dsn = gdb_path_out, layer = "Belfast_SA", verbose = FALSE)
belf_metr_area <- spTransform(belf_metr_area, "+init=epsg:4326")
leaflet(belf_metr_area) %>% addTiles() %>% addPolygons()
```

> Belfast's control zone

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#control zones
belf_control_zones <- read_belfcontrol_zone(dir_path)
leaflet(belf_control_zones) %>% addTiles() %>% addPolygons() 
```


```{r, echo=FALSE, warning=FALSE, message=FALSE}
#PSNI data
belf_data <- read_bel_data(dir_path)
belf_data <- rename(belf_data,c("X" = "Longitude","Y" = "Latitude"))
belf_control_data <- read_belf_controldata(dir_path)
```

> Time series Analysis

```{r,echo=FALSE, warning=FALSE,message=FALSE}
time_plot_belf(belf_data)
```


```{r,echo=FALSE, warning=FALSE,message=FALSE}
belfast_road_data <- read_belf_road(dir_path)
belfast_road_data@data <- rowid_to_column(belfast_road_data@data, "ID")
```


```{r,echo=FALSE, warning=FALSE,message=FALSE}
#Nearest line in streets that changed
nearest <- nearest_line_belf(belf_data,belfast_road_data)
nearest <- spTransform(nearest,"+init=epsg:4326")
#Merge the dataframes based on the ID of the nearest line in order to connect geoinformation
merged <- merge(data.frame(nearest), belfast_road_data@data,by.x = "nearest_line_id" ,by.y = "ID")
```

> Mapping accidents with roads: 2013

```{r, echo=FALSE, warning=FALSE, message=FALSE}
leaflet_map_belf(belfast_road_data, merged[merged$year == "2013", ])
belcount(merged[merged$year == "2013", ])
```

> Mapping accidents with roads: 2014

```{r, echo=FALSE, warning=FALSE, message=FALSE}
leaflet_map_belf(belfast_road_data,merged[merged$year == "2014", ])
belcount(merged[merged$year == "2014", ])
```

> Mapping accidents with roads: 2015

```{r, echo=FALSE, warning=FALSE, message=FALSE}
leaflet_map_belf(belfast_road_data,merged[merged$year == "2015", ])
belcount(merged[merged$year == "2015", ])
```

> Mapping accidents with roads: 2016

```{r,echo=FALSE, warning=FALSE, message=FALSE, comment=FALSE}
leaflet_map_belf(belfast_road_data,merged[merged$year == "2016", ])
belcount(merged[merged$year == "2016", ])
```

> Mapping accidents with roads: 2017

```{r,echo=FALSE, warning=FALSE, message=FALSE, comment=FALSE}
leaflet_map_belf(belfast_road_data,merged[merged$year == "2017", ])
belcount(merged[merged$year == "2017", ])
```

> Mapping accidents with roads: 2018

```{r, echo=FALSE, warning=FALSE, message=FALSE}
leaflet_map_belf(belfast_road_data,merged[merged$year == "2018", ])
belcount(merged[merged$year == "2018", ])
```

> Mapping accidents with roads: 2019

```{r, echo=FALSE, warning=FALSE, message=FALSE}
leaflet_map_belf(belfast_road_data,merged[merged$year == "2019", ])
belcount(merged[merged$year == "2019", ])
```

> Count pre 20mph

```{r, echo=FALSE, warning=FALSE, message=FALSE}
pre <- belcount_pre(merged[merged$a_date >= "2013-02-01" & merged$a_date <= "2016-01-31", ])
pre
```

> Count post 20mph

```{r, echo=FALSE, warning=FALSE, message=FALSE}
post <- belcount(merged[merged$a_date >= "2016-02-02" & merged$a_date <= "2019-12-31", ])
post
```

> Output column: Changed to 20 mph

```{r, echo=FALSE, warning=FALSE, message=FALSE}
head(merged[,c(25,13,36,37,41)])
```


```{r, echo=FALSE, warning=FALSE, message=FALSE}
#Link every accident with a zone
belf_data <- rename(belf_data,c("X" = "Longitude","Y" = "Latitude"))
total_zones <- buffer_data(belf_data , belf_impl_zones_out)
total_zones <- cbind(Zone_info = "Implementation zone", total_zones)
total_zones <- delete_na(total_zones,c("X_COORD" ,"Y_COORD"))
total_zones$a_type <- as.character(total_zones$a_type )
total_zones$a_type [total_zones$a_type  == 1] <- "fatal collision"
total_zones$a_type [total_zones$a_type  == 2] <- "Serious collision"
total_zones$a_type [total_zones$a_type  == 3] <- "Slight collision"
```

> Mapping accidents with zones: 2013

```{r, echo=FALSE, warning=FALSE, message=FALSE}
total <- total_zones[total_zones$a_date >="2013-01-01" & total_zones$a_date <= "2013-12-31", ]
#belf_leaflet_zones(belf_impl_zones_out,total)
not_changed <- delete_na(total_zones[!(total_zones$a_ID %in% merged$a_ID),],"a_ID")
leaflet_map_belf(belfast_road_data,not_changed)
s_13 <- nrow(buffer_data(total,belf_metr_area))
```

> Mapping accidents with zones: 2014

```{r, echo=FALSE, warning=FALSE, message=FALSE}
total <- total_zones[total_zones$a_date >="2014-01-01" & total_zones$a_date <= "2014-12-31", ]
#belf_leaflet_zones(belf_impl_zones_out,total)
not_changed <- delete_na(total_zones[!(total_zones$a_ID %in% total$a_ID),],"a_ID")
belf_leaflet_zones(belfast_road_data,not_changed)
s_14 <- nrow(buffer_data(total,belf_metr_area))
```

> Mapping accidents with zones: 2015

```{r, echo=FALSE, warning=FALSE, message=FALSE}
total <- total_zones[total_zones$a_date >="2015-01-01" & total_zones$a_date <= "2015-12-31", ]
#belf_leaflet_zones(belf_impl_zones_out,total)
not_changed <- delete_na(total_zones[!(total_zones$a_ID %in% total$a_ID),],"a_ID")
belf_leaflet_zones(belfast_road_data,not_changed)
s_15 <- nrow(buffer_data(total,belf_metr_area))
```

> Mapping accidents with zones: 2016

```{r, echo=FALSE, warning=FALSE, message=FALSE}
total <- total_zones[total_zones$a_date >="2016-01-01" & total_zones$a_date <= "2016-12-20", ]
#belf_leaflet_zones(belf_impl_zones_out,total)
not_changed <- delete_na(total_zones[!(total_zones$a_ID %in% total$a_ID),],"a_ID")
belf_leaflet_zones(belfast_road_data,not_changed)
s_16 <- nrow(buffer_data(total,belf_metr_area))
```

> Mapping accidents with zones: 2018

```{r, echo=FALSE, warning=FALSE, message=FALSE}
total <- total_zones[total_zones$a_date >="2018-03-06" & total_zones$a_date <= "2018-12-31", ]
#belf_leaflet_zones(belf_impl_zones_out,total)
not_changed <- delete_na(total_zones[!(total_zones$a_ID %in% total$a_ID),],"a_ID")
belf_leaflet_zones(belfast_road_data,not_changed)
s_18 <- nrow(buffer_data(total,belf_metr_area))
```

> Mapping accidents with zones: 2019

```{r, echo=FALSE, warning=FALSE, message=FALSE}
total <- total_zones[total_zones$year == "2019", ]
#belf_leaflet_zones(belf_impl_zones_out,total)
not_changed <- delete_na(total_zones[!(total_zones$a_ID %in% total$a_ID),],"a_ID")
belf_leaflet_zones(belfast_road_data,not_changed)
s_19 <- nrow(buffer_data(total,belf_metr_area))
```

> Total accidents in the implementation zone

```{r, echo=FALSE, warning=FALSE, message=FALSE}
s_13 + s_14 + s_15 + s_16 + s_18 + s_19 
```

> Table: Average annual road traffic collision rates in the city centre of Belfast

```{r,echo=FALSE,warning=FALSE,message=FALSE}
belf_annual_table(total_zones,merged,pre,post)
```


> Table: Average annual road traffic collision rates in the metropolitan area of Belfast

```{r, echo=FALSE, warning=FALSE, message=FALSE}

total_zones <- buffer_data(belf_data , belf_metr_area)
total_zones <- cbind(Zone_info = "Implementation zone", total_zones)
total_zones <- delete_na(total_zones,c("X_COORD" ,"Y_COORD"))
total_zones$a_type <- as.character(total_zones$a_type )
total_zones$a_type [total_zones$a_type  == 1] <- "fatal collision"
total_zones$a_type [total_zones$a_type  == 2] <- "Serious collision"
total_zones$a_type [total_zones$a_type  == 3] <- "Slight collision"


belf_annual_table(total_zones,merged,pre,post)
```





> Effect estimate ( GIS )

```{r,echo=FALSE,warning=FALSE,message=FALSE}
a <- c(nrow(total_zones[total_zones$a_date >= "2013-02-01" & total_zones$a_date <= "2014-01-31", ]))
b <- c(nrow(total_zones[total_zones$a_date >= "2014-02-01" & total_zones$a_date <= "2015-01-31", ]))
c <- c(nrow(total_zones[total_zones$a_date >= "2015-02-01" & total_zones$a_date <= "2016-01-31", ]))
e <- c(nrow(total_zones[total_zones$a_date >= "2016-02-02" & total_zones$a_date <= "2017-01-31", ]))
d <- c(nrow(total_zones[total_zones$a_date >= "2017-02-01" & total_zones$a_date <= "2018-01-31", ]))
h <- c(nrow(total_zones[total_zones$a_date >= "2018-02-01" & total_zones$a_date <= "2019-01-31", ]))
k <- c(nrow(total_zones[total_zones$a_date >= "2019-02-01" & total_zones$a_date <= "2019-12-31", ]))
sum1 <- (a+b+c)/3
sum2 <- (d + e + h + k) / 3.9 
unadjusted_estimate <-  (sum1 - sum2 ) / sum1  
trend_a <- (a-b) / a 
trend_b <- (b-c)/ b
secular_trend <- (trend_a + trend_b) / 2
f <- ( unadjusted_estimate - secular_trend ) * 100
Y_2013_14 <- c(a,round(a, digits = 2)," ",round(f,digits = 2))
Y_2014_15 <- c(b,b," "," ")
Y_2015_16 <- c(c,c," "," ")
Y_2016_17 <- c(e,round(e,digits = 2)," "," ")
Y_2017_18 <- c(d,round(d ,digits = 2)," "," ")
Y_2018_19 <- c(h,round(h  ,digits = 2)," "," ")
Y_2019_20 <- c(k,round(k / 0.9 ,digits = 2)," "," ")
Tax_year <- c("Annual number of collisions in roads changed to 20mph","Rate per year"," ","% reduction in collisions ")
df <- data.frame(Tax_year,Y_2013_14,Y_2014_15,Y_2015_16,Y_2016_17,Y_2017_18,Y_2018_19,Y_2019_20)
colnames(df)=c("Tax year", "2013/14","2014/15","2015/16","2016/17","2017/18", "2018/19", "2019/20")
kable(df,caption = "Effect estimate") %>% kable_styling(bootstrap_options = c("striped", "hover"))



calculations <- c("A + B + C / 3 "," D + E / 3.9 ", "A - B / A", "B - C / B", "Unadjusted_estimate", "Secular_trend" )
column <- c(round(sum1,digits = 2),round(sum2,digits = 2),round(trend_a,digits = 2) * 100, round(trend_b,digits = 2) * 100, round(unadjusted_estimate,digits = 2) *100,round(secular_trend, digits = 2 ) * 100)

df_cal <- data.frame(calculations,column)
colnames(df_cal) <-  c("Calculations", " ")
kable(df_cal) %>% kable_styling(position = "center",bootstrap_options = c("basic","hover","striped"),font_size = 15 )%>%  
    footnote(general = " ", number =c("A : accidents 2013/14 ( 1 year )","B : accidents 2014/15 ( 1 year ) ","C : accidents 2015/16 ( 1 year )","D : accidents 2018/19 ( 1 year )","E : accidents 2019/20 ( 11 months )"))

```

> Count accidents in Control Zone : City Center --> Central ( Ards )

```{r, echo=FALSE, warning=FALSE, message=FALSE}
belf_control_data <- rename(belf_control_data,c("X" = "Longitude","Y" = "Latitude"))
control_data_df <- buffer_data(belf_control_data,belf_control_zones)
control_data_df <- cbind(Zone_info = "Control zone", control_data_df)
leaflet(belf_control_zones) %>% addTiles() %>% addPolygons() %>% addMarkers(lng = control_data_df$Longitude,  lat = control_data_df$Latitude) %>% setView(lng = -5.69092, lat = 54.59236, zoom = 13)
nrow(control_data_df)
```

> Output column : Output Area code ( OA_code )

```{r, echo=FALSE, warning=FALSE, message=FALSE}
head(total_zones[,c(25,13,34)])
```

> Updated dataset for Belfast city

```{r, echo=FALSE, warning=FALSE, message=FALSE}
merged_1 <- merged[,-c(1,29:35,38:40,42:47)]
merged_1$a_time <- as.character(merged_1$a_time)
merged_1 <- rename(merged_1,c("X" = "Longitude","Y" = "Latitude"))
total_zones_1 <- total_zones[,-c(28:32)]
total_zones_1$a_time <- as.character(total_zones_1$a_time)
updated_dataset <- rbind.fill(merged_1,total_zones_1)
control_data_df$a_time <- as.character(control_data_df$a_time)
#final_dataset
final_df <- rbind.fill(updated_dataset,control_data_df)
final_df <- final_df[,-c(32,34:37)]
#Create new csv file with the cleaned data
write.csv(final_df, file = paste0(dir_path, "/Belfast/final_Belfast_data.csv"),row.names = FALSE)