---
title: "CIs"
author: "Kelly"
date: "2024-01-12"
output: html_document
---


Confidence intervals with exact poisson distribution for rates
Exact Poisson



```{r echo=FALSE,warning=FALSE,message=FALSE}

poisson.test(1082, conf.level = 0.95 )$conf.int

```

Normal approximation

```{r echo=FALSE,warning=FALSE,message=FALSE}
R_pre = 167
SE_pre = sqrt(R_pre)

k = 1.96
ci_lwr_pre = round(R_pre - (k*SE_pre),0)
ci_upr_pre = round(R_pre + (k*SE_pre),0)


```


CI for diff(rates), normal approximation


```{r echo=FALSE,warning=FALSE,message=FALSE}
R_pre = 705   
R_post = 923  

time_pre <- 
time_post <- 

SE_pre = sqrt(R_pre/time_pre)
SE_post = sqrt(R_post/time_post)

R_diff = R_post - R_pre
s = (SE_pre^2) + (SE_post^2)
SE_R_diff = sqrt(s)


k = 1.96
ci_lwr_pre = round(R_diff - (k*SE_R_diff),0)
ci_upr_pre = round(R_diff + (k*SE_R_diff),0)

ci_lwr_pre
ci_upr_pre
```


CI for diff(rates), normal approximation


```{r echo=FALSE,warning=FALSE,message=FALSE}
R_obs = 1082 
R_pred = 1306

time <- 

SE_obs = sqrt(R_obs/time)
SE_pred = sqrt(R_pred/time)

R_diff = R_pred - R_obs
s = (SE_obs^2) + (SE_pred^2)
SE_R_diff = sqrt(s)


k = 1.96
ci_lwr_pre = round(R_diff - (k*SE_R_diff),0)
ci_upr_pre = round(R_diff + (k*SE_R_diff),0)

R_diff
ci_lwr_pre
ci_upr_pre
```



delta method to find variance of  %diff


```{r echo=FALSE,warning=FALSE,message=FALSE}
R_pre = 144 #90 #rate pre  #observed
R_post = 112  #109 #rate post   #predicted

#roads
#post 3.42

#zones
#post  
#1a/1b: 3.42
#2/3: 2.83
#4/5: 2.63
#6: 1.83

time_pre <- 3   # always 3
time_post <- 2.83

R_diff = ((R_post-R_pre)/R_pre) * 100
#R_diff = ((R_post-R_pre)/R_post) * 100
R = R_pre ^2
#R = R_post ^2

Var_1 = R_pre / time_pre
Var_2 = R_post / time_post

A = Var_1 * (((100*R_post)/R)^2)
B = Var_2 * ((100/R_pre)^2)

Var_diff = A + B
SE_R_diff = sqrt(Var_diff) 

k = 1.96
ci_lwr = round(R_diff - (k*SE_R_diff),0)
ci_upr = round(R_diff + (k*SE_R_diff),0)

R_diff
ci_lwr
ci_upr
```

delta method to find variance of  %diff in GAM predicted vs observed


```{r echo=FALSE,warning=FALSE,message=FALSE}
R_obs = 90
R_pred = 109  


R_diff = ((R_pred-R_obs)/R_pred) * 100
R = R_pred^2

Var_1 = R_obs
Var_2 = R_pred

A = Var_1 * (((100*R_obs)/R)^2)
B = Var_2 * ((100/R_pred)^2)

Var_diff = A + B
SE_R_diff = sqrt(Var_diff) 

k = 1.96
ci_lwr = round(R_diff - (k*SE_R_diff),0)
ci_upr = round(R_diff + (k*SE_R_diff),0)

R_diff
ci_lwr
ci_upr
```

delta method to find variance of dif %diff  pre and post 20mph

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(readxl)
df = read_excel('C:/Users/Kyriaki Kokka/Desktop/EDINBURGH/20mph_tables_data.xlsx')

R_pre_imp = df$Rate_pre_imp
R_post_imp = df$Rate_post_imp
time_pre <- df$time_pre

R_pre_con =   df$Rate_pre_con
R_post_con = df$Rate_post_con
time_post <- df$time_post

df$diff_imp = 100 * (R_post_imp - R_pre_imp) / R_pre_imp
df$diff_con =  100 * (R_post_con - R_pre_con) / R_pre_con

df$D_diff = df$diff_imp - df$diff_con
#D_diff = diff_imp - diff_con

Var_1 = R_pre_imp / time_pre
Var_2 = R_post_imp / time_post

SE_D = sqrt(Var_1 + Var_2)
k = 1.96
D = R_post_imp - R_pre_imp 
df$ci_lwr_D = D - (k*SE_D)
df$ci_upr_D = D + (k*SE_D)

R_imp = R_pre_imp ^2

A_imp = Var_1 * (((100*R_post_imp)/R_imp)^2)
B_imp = Var_2 * ((100/R_pre_imp)^2)

Var_diff_imp = A_imp + B_imp
SE_R_diff_imp = sqrt(Var_diff_imp) 

k = 1.96
df$ci_lwr_dif_imp = diff_imp - (k*SE_R_diff_imp)
df$ci_upr_dif_imp = diff_imp + (k*SE_R_diff_imp)


#control
Var_3 = R_pre_con / time_pre
Var_4 = R_post_con / time_post
R_con = R_pre_con ^2

A_con = Var_3 * (((100*R_post_con)/R_con)^2)
B_con = Var_4 * ((100/R_pre_con)^2)

Var_diff_con = A_con + B_con
SE_R_diff_con = sqrt(Var_diff_con) 

df$ci_lwr_dif_con = diff_con - (k*SE_R_diff_con)
df$ci_upr_dif_con = diff_con + (k*SE_R_diff_con)


SE_D_diff = sqrt(Var_diff_con + Var_diff_imp)


D 
df$ci_lwr_D = round(df$ci_lwr_D, 0)
df$ci_upr_D = round(df$ci_upr_D,0)


k = 1.96
df$ci_lwr_D_diff = round(D_diff - (k*SE_D_diff), 0)
df$ci_upr_D_diff = round(D_diff + (k*SE_D_diff), 0)

df$diff_imp = round(df$diff_imp, 0)
df$ci_lwr_dif_imp = round(df$ci_lwr_dif_imp, 0) 
df$ci_upr_dif_imp  = round(df$ci_upr_dif_imp ,0)

df$diff_con = round(df$diff_con,0)
df$ci_lwr_dif_con = round(df$ci_lwr_dif_con,0) 
df$ci_upr_dif_con = round(df$ci_upr_dif_con ,0)

df$D_diff = round(D_diff,0)
df$ci_lwr_D_diff = round(df$ci_lwr_D_diff,0)
df$ci_upr_D_diff = round(df$ci_upr_D_diff,0)


round(D_diff,0)
round(df$ci_lwr_D_diff,0)
round(df$ci_upr_D_diff,0)


write.csv(df, file = "C:/Users/Kyriaki Kokka/Desktop/EDINBURGH/20mph_tables_data_CIs.csv",row.names = FALSE)


head(df)
```

for when you don't have a fixed total time
pre vs post

```{r echo=FALSE,warning=FALSE,message=FALSE}

R_pre = 1022
L_pre = 960
U_pre = 1087

R_post = 705 
L_post = 654
U_post = 759

Dif = R_post - R_pre
diff = 100 * (R_post - R_pre) / R_pre


SE_pre = ( U_pre - L_pre ) / 3.92
SE_post = ( U_post - L_post ) / 3.92

Var_pre = SE_pre ^ 2
Var_post = SE_post ^ 2

SE = sqrt(Var_pre + Var_post)

ci_lwr_D = Dif - (k*SE)
ci_upr_D = Dif + (k*SE)

R = R_pre ^ 2

Var_1 <- SE_pre ^ 2
Var_2 <- SE_post ^ 2

A = Var_1 * (((100*R_post)/R)^2)
B = Var_2 * ((100/R_pre)^2)


Var_diff = A + B
SE_R_diff = sqrt(Var_diff) 

k = 1.96
ci_lwr_dif = diff - (k*SE_R_diff)
ci_upr_dif = diff + (k*SE_R_diff)

Dif
ci_lwr_D
ci_upr_D

diff
ci_lwr_dif
ci_upr_dif

#Var_diff

```


for when you don't have a fixed total time
obs vs pred


```{r echo=FALSE,warning=FALSE,message=FALSE}

R_obs = 4.7
L_obs = 2
U_obs = 13

R_pred =  4.9 
L_pred = 2
U_pred = 12

Dif = R_pred - R_obs
diff = 100 * (R_pred - R_obs) / R_pred


SE_obs = ( U_obs - L_obs ) / 3.92
SE_pred = ( U_pred - L_pred ) / 3.92

Var_obs = SE_obs ^ 2
Var_pred = SE_pred ^ 2

k = 1.96

SE_dif = sqrt(Var_obs + Var_pred)

ci_lwr_D = Dif - (k*SE_dif)
ci_upr_D = Dif + (k*SE_dif)

R = R_pred ^ 2


A = Var_pred * (((100*R_obs)/R)^2)
B = Var_obs * ((100/R_pred)^2)


Var_diff = A + B
SE_R_diff = sqrt(Var_diff) 

k = 1.96
ci_lwr_dif = diff - (k*SE_R_diff)
ci_upr_dif = diff + (k*SE_R_diff)

Dif
ci_lwr_D
ci_upr_D

diff
ci_lwr_dif
ci_upr_dif
```

